TBD

### 2016-10-17 paper.tex
improved LS section

\begin{equation}
\label{eq:vis_definition}
d_{pq} = g_{p}\conj{g}_{q}y_{pq} + n_{pq},
\end{equation}
where $g_{p}$ and $g_{q}$ are the direction independent gains associated with antenna $p$ and $q$, $y_{pq}$ denotes the true visibility that baseline $pq$ measured
and $n_{pq}$ is the thermal noise component. Conjugation is denoted by $\conj{(*)}$. During the course of an actual observation the true value of $g_p$, $g_q$ and $y_{pq}$ are unknown and are the quantities which infact have 
to be estimated.

@@

\subsection{Signal-to-noise Ratio}
If the array is redundant and the function $\phi_{ij}$ is known we can rewrite Eq.~\eqref{eq:vis_definition} as
\begin{equation}
\label{eq:vis_red}
d_{pq} = g_{p}\conj{g}_{q}y_{\phi_{pq}} + n_{pq}.
\end{equation}
Eq.~\eqref{eq:vis_red} can also be expressed in the following vector form 
\begin{equation}
\bd = \bv + \bn, 
\end{equation}
where 
\begin{align}
 \left [ \bd \right]_{\alpha_{pq}} &= d_{pq}, & \left [ \bv \right ]_{\alpha_{pq}} &= g_p y_{\phi_{pq}} \conj{g}_q\nonumber\\
 \left [ \bn \right ]_{\alpha_{pq}} &= n_{pq}. &  &\label{eq:vec_definitions}
\end{align}
In Eq.~\eqref{eq:vec_definitions}, the size of the three vectors are equal to $B$ (i.e. $p<q$), which denotes the number of baselines in the array. Moreover,
\begin{equation}
\alpha_{pq} =
\begin{cases}
(q-p) + (p-1)\left (N-\frac{1}{2}p \right ) & \textrm{if}~p<q\\
B + (p-q) + (q-1)\left (N-\frac{1}{2}q \right )) & \textrm{if}~p>q\\
%B+q + \frac{1}{2}(p-1)(p-2) & \textrm{if}~p>q\\
0 & \textrm{otherwise}
\end{cases}.
\end{equation}
The easiest way to construct the vectors in Eq.~\ref{eq:vec_definitions} is to enumerate through the composite indexes $pq$ in the following order $12, 13,\cdots,1N,23,\cdots$.
For each composite index we then compute the right hand side of the appropriate vector element definition which we then need to assign to the 
correct vector position. The correct position is calculated with $\alpha_{pq}$. Using the aforementioned order, however, allows you to fill the vector in numerical order, i.e. $12,13,\cdots,1N,23,\cdots \xrightarrow{\alpha_{pq}} 1,2,3,\cdots,B$.

@@

We use Eq.~\eqref{eq:GN_update} or Eq.~\eqref{eq:LM_update} to iteratively update our 
parameter vector as follows:
\begin{equation}
\label{eq:update}
\breve{\bz}_{k+1} \gets \breve{\bz}_{k} + \Delta \breve{\bz}_{k}. 
\end{equation}
We update our parameter vector by using Eq.~\eqref{eq:update} until convergence is reached. To improve readability we do not explicitly denote the iteration subscript $k$ in 
Eq.~\eqref{eq:GN_update} and Eq.~\eqref{eq:LM_update}.

\subsection{Redundant Jacobian and Hessian}
If we apply the definition in Eq.~\eqref{eq:Jacobian} to Eq.~\eqref{eq:least_squares_complex} we obtain the following analytic result:
\begin{equation}
\label{eq:Jacobian_red}
\bJ = \begin{bmatrix}
       \bM & \bN\\
       \conj{\bN} & \conj{\bM}
      \end{bmatrix},
\end{equation}
where
\begin{equation}
\bM =\begin{bmatrix}
      \bO & \bP
     \end{bmatrix},
\end{equation}
and 
\begin{equation}
\bN = \begin{bmatrix}
       \bQ & \bzero
      \end{bmatrix}.
\end{equation}
Moreover,
\begin{align}
\left [ \bM_1 \right ]_{\alpha_{pq},j} &= y_{\phi_{pq}}\conj{g}_q\delta_p^j, & \left [ \bM_2 \right ]_{\alpha_{pq},j} &= g_p\conj{g}_q\delta_{\phi_{pq}}^j 
\end{align}
and
\begin{equation}
\left [ \bN_1 \right ]_{\alpha_{pq},j} = g_py_{\phi_{pq}}\delta^j_q. 
\end{equation}

It is now trivial to compute the Hessian $\bJ^H\bJ$ by using Eq.~\eqref{eq:Jacobian_red}. If we substitute Eq.~\eqref{eq:Jacobian_red} into $\bJ^H\bJ$
we obtain 
\begin{equation}
\label{eq:red_H}
\bH = \bJ^H\bJ = 
\begin{bmatrix}
\bA & \bB\\
\conj{\bB} & \conj{\bA}
\end{bmatrix},
\end{equation}
where

@@

\begin{equation}
[\bE]_{ij} = 
\begin{cases}
 \sum_{pq \in \mathcal{PQ}_i} \left | g_p \right |^2 \left | g_q \right |^2  & \textrm{if} ~ i=j\\
 0 & \textrm{otherwise}
\end{cases},
\end{equation}
\begin{equation}
[\bF]_{ij} = 
\begin{cases}
 g_i g_j  \left | y_{\zeta_{ij}} \right |^2  & \textrm{if} ~ i \neq j\\
 0 & \textrm{otherwise}
\end{cases},
\end{equation}
and
\begin{equation}
[\boldsymbol{G}]_{ij} = 
\begin{cases}
 g_i y_j  \left | g_{\xi_{ij}} \right |^2  & \textrm{if} ~ \xi_{ij}\neq0\\
 0 & \textrm{otherwise}
\end{cases}.
\end{equation}

Moreover, $(*)^T$ denotes matrix transposition and

\begin{equation}
\mathcal{PQ}_i = \left\{pq\in\mathbb{N}^2|(\phi_{pq} = i) \right\}.
\end{equation}

HAVE TO MAKE SURE I DEFINE ALL THE MATH SYMBOLS THAT I USE. IF NOT HERE THEN EARLIER....

Furthermore, substituting Eq.~\eqref{eq:Jacobian_red} into $\bJ^H\breve{\br}$ results in
\begin{equation}
\bJ^H\breve{\br} = \begin{bmatrix}
                   \ba & \bb & \conj{\ba} & \conj{\bb}\\
                   \end{bmatrix}^T,
\end{equation}
where
\begin{align}
\label{eq:ab}
\left [ \ba \right ]_i &= \sum_{k\neq i} g_k \widetilde{y}_{ik}r_{ik},  & \left [ \bb \right ]_i &= \sum_{pq\in\mathcal{PQ}_i}\conj{g}_p g_q r_{pq},
\end{align}
and
\begin{equation}
\widetilde{y}_{ik} = 
\begin{cases}
\conj{y}_{\zeta_{ik}} & \textrm{if}~k > i\\
y_{\zeta_{ik}} & \textrm{otherwise}
\end{cases}.
\end{equation}

HAVE TO RECHECK THE ABOVE EQUATIONS DIRECTLY FROM THE CODE.

HAVE TO STATE WHETHER COLUMN OR ROW VECTOR.

@@

Replacing $\breve{\br}$ with $\breve{\bd}-\breve{\bv}$ in Eq.~\eqref{eq:GN_update} results in
\begin{equation}
\label{eq:temp_GN_eq}
\Delta \breve{\bz} = (\bJ^H\bJ)^{-1}\bJ^H(\breve{\bd}-\breve{\bv}), 
\end{equation}
Substituting the first identity of Eq.~\eqref{eq:identities} into Eq.~\eqref{eq:temp_GN_eq} and simplifying we obtain
\begin{equation}
\label{eq:one_thrid}
\Delta \breve{\bz} = (\bJ^H\bJ)^{-1}\bJ^H\breve{\bd}-\frac{1}{3}\breve{\bz}.
\end{equation}
It now trivially follows from Eq.~\eqref{eq:one_thrid} that:
\begin{equation}
\label{eq:two_thrids}
\breve{\bz}_{k+1} = (\bJ^H\bJ)^{-1}\bJ^H\breve{\bd} + \frac{2}{3}\breve{\bz}_{k}. 
\end{equation}
%STILL NEED TO ADD z k+1 EXPRESSION.
THE TAKE HOME HERE IS WE CAN CALCULATE THE UPDATE STEP WITHOUT CALCULATING THE RESIDUAL.

>>>>

\begin{equation}
\label{eq:vis_definition}
d_{pq} = g_{p}\conj{g_q}y_{pq} + n_{pq},
\end{equation}
where $g_{p}$ and $g_{q}$ are the direction independent gains associated with antenna $p$ and $q$, $y_{pq}$ denotes the true visibility that baseline $pq$ measured
and $n_{pq}$ is the thermal noise component. Conjugation is denoted by $\conj{(*)}$. During the course of an actual observation the true value of $g_p$, $g_q$ and $y_{pq}$ are unknown and are the quantities which infact have 
to be estimated.

@@

\subsection{Signal-to-noise Ratio}
If the array is redundant and the function $\phi_{ij}$ is known we can rewrite Eq.~\eqref{eq:vis_definition} as
\begin{equation}
\label{eq:vis_red}
d_{pq} = g_{p}\conj{g_q}y_{\phi_{pq}} + n_{pq}.
\end{equation}
Eq.~\eqref{eq:vis_red} can also be expressed in the following vector form 
\begin{equation}
\bd = \bv + \bn, 
\end{equation}
where 
\begin{align}
 \left [ \bd \right]_{\alpha_{pq}} &= d_{pq}, & \left [ \bv \right ]_{\alpha_{pq}} &= g_p y_{\phi_{pq}} \conj{g_q}\nonumber\\
 \left [ \bn \right ]_{\alpha_{pq}} &= n_{pq}. &  &\label{eq:vec_definitions}
\end{align}
In Eq.~\eqref{eq:vec_definitions}, the size of the three vectors are equal to $B$ (i.e. $p<q$), which denotes the number of baselines in the array. Moreover,
\begin{equation}
\alpha_{pq} =
\begin{cases}
(q-p) + (p-1)\left (N-\frac{1}{2}p \right ) & \textrm{if}~p<q\\
B + (p-q) + (q-1)\left (N-\frac{1}{2}q \right )) & \textrm{if}~p>q\\
%B+q + \frac{1}{2}(p-1)(p-2) & \textrm{if}~p>q\\
0 & \textrm{otherwise}
\end{cases}.
\end{equation}
The easiest way to construct the vectors in Eq.~\ref{eq:vec_definitions} is to enumerate through the composite indexes $pq$ in the following order $12, 13,\cdots,1N,23,\cdots$.
For each composite index we then compute the right hand side of the appropriate vector element definition which we then need to assign to the 
correct vector position. The correct position is calculated with $\alpha_{pq}$. Using the aforementioned order, however, allows you to fill the vector in numerical order, i.e. $12,13,\cdots,1N,23,\cdots \xrightarrow{\alpha_{pq}} 1,2,3,\cdots,B$.

@@

We use Eq.~\eqref{eq:GN_update} or Eq.~\eqref{eq:LM_update} to iteratively update our 
parameter vector as follows:
\begin{equation}
\label{eq:update}
\breve{\bz}_{k+1} = \breve{\bz}_{k} + \Delta \breve{\bz}_{k}. 
\end{equation}
We update our parameter vector by using Eq.~\eqref{eq:update} until convergence is reached. To improve readability we do not explicitly denote the iteration subscript $k$ in 
Eq.~\eqref{eq:GN_update} and Eq.~\eqref{eq:LM_update}.

\subsection{Analytic Expressions}
If we apply the definition in Eq.~\eqref{eq:Jacobian} to Eq.~\eqref{eq:least_squares_complex} we obtain the following analytic result:
\begin{equation}
\label{eq:Jacobian_red}
\bJ = \begin{bmatrix}
       \bM & \bN\\
       \conj{\bN} & \conj{\bM}
      \end{bmatrix},
\end{equation}
where
\begin{equation}
\bM =\begin{bmatrix}
      \bO & \bP
     \end{bmatrix},
\end{equation}
and 
\begin{equation}
\bN = \begin{bmatrix}
       \bQ & \bzero
      \end{bmatrix}.
\end{equation}
Moreover,
\begin{equation}
\left [ \bO  \right ]_{\alpha_{pq},j} = \begin{cases}
                                         y_{\phi_{pq}}\conj{g_q} & \textrm{if}~p=j\\
                                         0  & \textrm{otherwise} 
                                        \end{cases},
\end{equation}

\begin{equation}
\left [ \bP  \right ]_{\alpha_{pq},j} = \begin{cases}
                                         g_p\conj{g_q} & \textrm{if}~\phi_{pq}=j\\
                                         0  & \textrm{otherwise} 
                                        \end{cases}
\end{equation}
and
\begin{equation}
\left [ \bQ  \right ]_{\alpha_{pq},j} = \begin{cases}
                                         g_py_{\phi_{pq}} & \textrm{if}~q=j\\
                                         0  & \textrm{otherwise} 
                                        \end{cases}
\end{equation}

%\begin{align}
%\left [ \bM_1 \right ]_{\alpha_{pq},j} &= y_{\phi_{pq}}\conj{g_q}\delta_p^j, & \left [ \bM_2 \right ]_{\alpha_{pq},j} &= g_p\conj{g_q}\delta_{\phi_{pq}}^j 
%\end{align}
%\begin{equation}
%\left [ \bN_1 \right ]_{\alpha_{pq},j} = g_py_{\phi_{pq}}\delta^j_q. 
%\end{equation}

It is now trivial to compute the Hessian $\bH$ by using Eq.~\eqref{eq:Jacobian_red}. If we substitute Eq.~\eqref{eq:Jacobian_red} into $\bJ^H\bJ$
we obtain 
\begin{equation}
\label{eq:red_H}
\bH = \bJ^H\bJ = 
\begin{bmatrix}
\bA & \bB\\
\conj{\bB} & \conj{\bA}
\end{bmatrix},
\end{equation}
where

@@

\begin{equation}
[\bE]_{ij} = 
\begin{cases}
 \sum_{pq \in \mathcal{PQ}_i} \left | g_p \right |^2 \left | g_q \right |^2  & \textrm{if} ~ i=j\\
 0 & \textrm{otherwise}
\end{cases},
\end{equation}
\begin{equation}
[\bF]_{ij} = 
\begin{cases}
 g_i g_j  \left | y_{\zeta_{ij}} \right |^2  & \textrm{if} ~ i \neq j\\
 0 & \textrm{otherwise}
\end{cases},
\end{equation}
and
\begin{equation}
[\boldsymbol{G}]_{ij} = 
\begin{cases}
 g_i y_j  \left | g_{\xi_{ij}} \right |^2  & \textrm{if} ~ \xi_{ij}\neq0\\
 0 & \textrm{otherwise}
\end{cases}.
\end{equation}
Moreover, $(*)^T$ denotes matrix transposition and
\begin{equation}
\mathcal{PQ}_i = \left\{pq\in\mathbb{N}^2|(\phi_{pq} = i) \right\}.
\end{equation}

Furthermore, substituting Eq.~\eqref{eq:Jacobian_red} into $\bJ^H\breve{\br}$ results in
\begin{equation}
\bJ^H\breve{\br} = \begin{bmatrix}
                   \ba \\
                   \bb \\
                   \conj{\ba}\\
                   \conj{\bb}
                   \end{bmatrix},
\end{equation}
where
\begin{align}
\label{eq:ab}
\left [ \ba \right ]_i &= \sum_{k\neq i} g_k \widetilde{y}_{ik}r_{ik},  & \left [ \bb \right ]_i &= \sum_{pq\in\mathcal{PQ}_i}\conj{g}_p g_q r_{pq},
\end{align}
and
\begin{equation}
\widetilde{y}_{ik} = 
\begin{cases}
\conj{y}_{\zeta_{ik}} & \textrm{if}~k > i\\
y_{\zeta_{ik}} & \textrm{otherwise}
\end{cases}.
\end{equation}
Moreover $\ba$ and $\bb$ are both column vectors.

HAVE TO RECHECK THE ABOVE EQUATIONS DIRECTLY FROM THE CODE.
DEFINED ALL OPERATORS AND SYMBOLS?

@@

Replacing $\breve{\br}$ with $\breve{\bd}-\breve{\bv}$ in Eq.~\eqref{eq:GN_update} results in
\begin{equation}
\label{eq:temp_GN_eq}
\Delta \breve{\bz} = (\bJ^H\bJ)^{-1}\bJ^H(\breve{\bd}-\breve{\bv}), 
\end{equation}
Substituting the first identity of Eq.~\eqref{eq:identities} into Eq.~\eqref{eq:temp_GN_eq} and simplifying the result 
\begin{equation}
\label{eq:one_thrid}
\Delta \breve{\bz} = (\bJ^H\bJ)^{-1}\bJ^H\breve{\bd}-\frac{1}{3}\breve{\bz}.
\end{equation}
It now trivially follows that:
\begin{equation}
\label{eq:two_thrids}
\breve{\bz}_{k+1} = (\bJ^H\bJ)^{-1}\bJ^H\breve{\bd} + \frac{2}{3}\breve{\bz}_{k}. 
\end{equation}
Eq.~\eqref{eq:two_thrids} shows us that in the case of redundant calibration we can calculate the GN update step without calculating the residual. The 
normal skymodel-based equivalent of Eq.~\eqref{eq:two_thrids} is equal to \citep{Smirnov2015}:
\begin{equation}
\label{eq:one_half}
\breve{\bg}_{k+1} = (\bJ^H\bJ)^{-1}\bJ^H\breve{\bd} + \frac{1}{2}\breve{\bg}_{k}, 
\end{equation}
where $\breve{\bg} = [\bg^T,\conj{\bg}^T]^T$

FIX TRANSPOSE PROBLEM
